Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-06-07 supp_mat_complexity_selection.Rmd
considering going back to GAMM models for fitting, since the toolkit is available for everything in the 'gsg' package.

# Use parametric bootstrapping to get confidence intervals for selection gradients
boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)

@@

# Use parametric bootstrapping to get confidence intervals for selection gradients
boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=10)

@@

```{r}
## Custom function to calculate relative fitness intervals for my models
relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
  model_null <- model.matrix(~1, newdata)

  get_relative_fitness <- function(.) {
  #mean_fitness <- mean(inverse_logit(model_null %*% fixef(.))) #fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
  absolute_fitness #/ mean_fitness # mean(absolute_fitness) # 
  }

  get_bootstraps <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])

  mean_fitness <- mean(get_relative_fitness(logistic_model))

  return(data.frame(relative_fitness = get_relative_fitness(logistic_model)/mean_fitness,
                    lower_2.5 = get_intervals[1, ]/mean_fitness,
                    upper_97.5 = get_intervals[2, ]/mean_fitness,
                    newdata))
}
```

@@

```{r}
RF_treatment_gall_size <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = seq(min(treatment_df$sc.gall_size),
                        max(treatment_df$sc.gall_size),
                        length.out = 100),
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=200)

@@

RF_control_gall_size <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = seq(min(control_df$sc.gall_size),
                        max(control_df$sc.gall_size),
                        length.out = 100),
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=200)

@@

bind_rows(mutate(RF_treatment_gall_size, Treatment = "Simple"),
          mutate(RF_control_gall_size, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_line() +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
```

```{r}
RF_treatment_clutch_size <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(min(treatment_df$sc.clutch_size),
                          max(treatment_df$sc.clutch_size),
                          length.out = 100),
     sc.female_preference = 0),
  bootstraps=200)

mean(RF_treatment_clutch_size$relative_fitness)

RF_control_clutch_size <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(min(control_df$sc.clutch_size),
                        max(control_df$sc.clutch_size),
                        length.out = 100),
     sc.female_preference = 0),
  bootstraps=200)

mean(RF_control_clutch_size$relative_fitness)

bind_rows(mutate(RF_treatment_clutch_size, Treatment = "Simple"),
          mutate(RF_control_clutch_size, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_line() +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
```

```{r}
RF_treatment_female_preference <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = seq(min(treatment_df$sc.female_preference),
                                max(treatment_df$sc.female_preference),
                                length.out = 100)),
  bootstraps=200)

@@

RF_control_female_preference <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = seq(min(control_df$sc.female_preference),
                                max(control_df$sc.female_preference),
                                length.out = 100)),
  bootstraps=200)

@@

bind_rows(mutate(RF_treatment_female_preference, Treatment = "Simple"),
          mutate(RF_control_female_preference, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=relative_fitness, color=Treatment, fill=Treatment)) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_line() +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5) +
```

@@

bind_rows(mutate(visreg(glmer_treatment, xvar="sc.female_preference", scale="response", plot=F)$fit, 
                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
          mutate(visreg(glmer_control, xvar="sc.female_preference", scale="response", plot=F)$fit, 
                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
  ggplot(., aes(x=sc.female_preference, y=`Relative fitness`, color=Treatment)) +
  geom_line() +
  scale_x_continuous(limits = c(HPDinterval_female_preference[1], HPDinterval_female_preference[2]))
```

@@

bind_rows(mutate(visreg(glmer_treatment, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
          mutate(visreg(glmer_control, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
  ggplot(., aes(x=sc.clutch_size, y=`Relative fitness`, color=Treatment)) +
  geom_line() +
  scale_x_continuous(limits = c(HPDinterval_clutch_size[1], HPDinterval_clutch_size[2]))
```

@@

@@

@@

@@

>>>>

# Use parametric bootstrapping to get confidence intervals for selection gradients
boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)

@@

# Use parametric bootstrapping to get confidence intervals for selection gradients
boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)

@@

```{r}
## Custom function to calculate relative fitness intervals for my models
relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)

  get_absolute_fitness <- function(.) {
  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
  absolute_fitness 
  }

  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])

  mean_fitness <- mean(get_absolute_fitness(logistic_model))

  return(data.frame(relative_fitness = get_absolute_fitness(logistic_model)/mean_fitness,
                    lower_2.5 = get_intervals[1, ]/mean_fitness,
                    upper_97.5 = get_intervals[2, ]/mean_fitness,
                    newdata))
}
```

@@

```{r}
HPD_50_treatment_size <- coda::HPDinterval(coda::as.mcmc(treatment_df$sc.gall_size), prob=0.5)
HPD_50_control_size <- coda::HPDinterval(coda::as.mcmc(control_df$sc.gall_size), prob=0.5)

HPD_95_treatment_size <- coda::HPDinterval(coda::as.mcmc(treatment_df$sc.gall_size), prob=0.95)
HPD_95_control_size <- coda::HPDinterval(coda::as.mcmc(control_df$sc.gall_size), prob=0.95)

RF_treatment_gall_size <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = treatment_df$sc.gall_size, 
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=1000)

@@

RF_control_gall_size <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = treatment_df$sc.gall_size,
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=1000)

@@

bind_rows(mutate(treatment_df, Treatment = "Simple"),
          mutate(control_df, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, color=Treatment, fill=Treatment)) +
  geom_density(alpha=0.5)

bind_rows(mutate(RF_treatment_gall_size, Treatment = "Simple"),
          mutate(RF_control_gall_size, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_line(aes(color=Treatment), size=0.25) +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
  geom_line(data = filter(mutate(RF_treatment_gall_size, Treatment = "Simple"), 
                          between(sc.gall_size, HPD_95_treatment_size[1], HPD_95_treatment_size[2])),
            aes(color=Treatment), size=1) +
  geom_line(data = filter(mutate(RF_control_gall_size, Treatment = "Complex"), 
                          between(sc.gall_size, HPD_95_control_size[1], HPD_95_control_size[2])), 
            aes(color=Treatment), size=1) +
    geom_line(data = filter(mutate(RF_treatment_gall_size, Treatment = "Simple"), 
                          between(sc.gall_size, HPD_50_treatment_size[1], HPD_50_treatment_size[2])),
            aes(color=Treatment), size=2.5) +
  geom_line(data = filter(mutate(RF_control_gall_size, Treatment = "Complex"), 
                          between(sc.gall_size, HPD_50_control_size[1], HPD_50_control_size[2])), 
            aes(color=Treatment), size=2.5) +
  ylab("Relative fitness") +
  xlab("Gall size (mm)")
```

```{r}
## Get Highest Posterior Density Intervals for clutch size phenotype

# 50%
HPD_50_treatment_clutch <- coda::HPDinterval(coda::as.mcmc(
  distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.5)
HPD_50_control_clutch <- coda::HPDinterval(coda::as.mcmc(
  distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.5)

# 95%
HPD_95_treatment_clutch <- coda::HPDinterval(coda::as.mcmc(
  distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.95)
HPD_95_control_clutch <- coda::HPDinterval(coda::as.mcmc(
  distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.95)

RF_treatment_clutch_size <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
     sc.female_preference = 0),
  bootstraps=1000)

# confirm that mean relative fitness = 1
mean(RF_treatment_clutch_size$relative_fitness)

RF_control_clutch_size <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
     sc.female_preference = 0),
  bootstraps=1000)

# confirm that mean relative fitness = 1
mean(RF_control_clutch_size$relative_fitness)

bind_rows(mutate(RF_treatment_clutch_size, Treatment = "Simple"),
          mutate(RF_control_clutch_size, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=relative_fitness)) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_line(aes(color=Treatment), size=0.25) +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
  geom_line(data = filter(mutate(RF_treatment_clutch_size, Treatment = "Simple"), 
                          between(sc.clutch_size, HPD_95_treatment_clutch[1], HPD_95_treatment_clutch[2])),
            aes(color=Treatment), size=1) +
  geom_line(data = filter(mutate(RF_control_clutch_size, Treatment = "Complex"), 
                          between(sc.clutch_size, HPD_95_control_clutch[1], HPD_95_control_clutch[2])), 
            aes(color=Treatment), size=1) +
    geom_line(data = filter(mutate(RF_treatment_clutch_size, Treatment = "Simple"), 
                          between(sc.clutch_size, HPD_50_treatment_clutch[1], HPD_50_treatment_clutch[2])),
            aes(color=Treatment), size=2.5) +
  geom_line(data = filter(mutate(RF_control_clutch_size, Treatment = "Complex"), 
                          between(sc.clutch_size, HPD_50_control_clutch[1], HPD_50_control_clutch[2])), 
            aes(color=Treatment), size=2.5) +
  ylab("Relative fitness") +
  xlab("Clutch size")
```

```{r}
## Get Highest Posterior Density Intervals for clutch size phenotype

# 50%
HPD_50_treatment_preference <- coda::HPDinterval(coda::as.mcmc(
  distinct(treatment_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.5)
HPD_50_control_preference <- coda::HPDinterval(coda::as.mcmc(
  distinct(control_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.5)

# 95%
HPD_95_treatment_preference <- coda::HPDinterval(coda::as.mcmc(
  distinct(treatment_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.95)
HPD_95_control_preference <- coda::HPDinterval(coda::as.mcmc(
  distinct(control_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.95)

RF_treatment_female_preference <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference), 
  bootstraps=1000)

@@

RF_control_female_preference <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference), 
  bootstraps=1000)

@@

bind_rows(mutate(RF_treatment_female_preference, Treatment = "Simple"),
          mutate(RF_control_female_preference, Treatment = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=relative_fitness)) +
    geom_hline(yintercept=1, linetype="dotted") +
  geom_line(aes(color=Treatment), size=0.25) +
  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
  geom_line(data = filter(mutate(RF_treatment_female_preference, Treatment = "Simple"), 
                          between(sc.female_preference, HPD_95_treatment_preference[1], HPD_95_treatment_preference[2])),
            aes(color=Treatment), size=1) +
  geom_line(data = filter(mutate(RF_control_female_preference, Treatment = "Complex"), 
                          between(sc.female_preference, HPD_95_control_preference[1], HPD_95_control_preference[2])), 
            aes(color=Treatment), size=1) +
    geom_line(data = filter(mutate(RF_treatment_female_preference, Treatment = "Simple"), 
                          between(sc.female_preference, HPD_50_treatment_preference[1], HPD_50_treatment_preference[2])),
            aes(color=Treatment), size=2.5) +
  geom_line(data = filter(mutate(RF_control_female_preference, Treatment = "Complex"), 
                          between(sc.female_preference, HPD_50_control_preference[1], HPD_50_control_preference[2])), 
            aes(color=Treatment), size=2.5) +
  ylab("Relative fitness") +
  xlab("Female preference")
```

```{r}
RF_treatment_clutch_preference <- relative_fitness_intervals(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
     sc.female_preference = distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference), 
  bootstraps=100)

mean(RF_treatment_clutch_preference$relative_fitness)

RF_control_clutch_preference <- relative_fitness_intervals(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference), 
  bootstraps=100)

mean(RF_control_clutch_preference$relative_fitness)

bind_rows(mutate(RF_treatment_clutch_preference, Treatment="Simple"),
          mutate(RF_control_clutch_preference, Treatment="Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=sc.female_preference, fill=relative_fitness)) +
  geom_raster(size=2) + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Relative fitness") +
  xlab("Clutch size") +
  ylab("Female preference")

expand.grid(sc.gall_size = 0,
     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference) %>%
  ggplot(., aes(x=sc.clutch_size, y=sc.female_preference)) +
  geom_point(shape=21)
```

@@

bind_rows(mutate(visreg(glmer_treatment, xvar="sc.female_preference", scale="response", plot=F)$fit, 
                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
          mutate(visreg(glmer_control, xvar="sc.female_preference", scale="response", plot=F)$fit, 
                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
  ggplot(., aes(x=sc.female_preference, y=`Relative fitness`, color=Treatment)) +
  geom_line() +
  scale_x_continuous(limits = c(HPDinterval_female_preference[1], HPDinterval_female_preference[2]))
```

@@

bind_rows(mutate(visreg(glmer_treatment, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
          mutate(visreg(glmer_control, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
  ggplot(., aes(x=sc.clutch_size, y=`Relative fitness`, color=Treatment)) +
  geom_line() +
  scale_x_continuous(limits = c(HPDinterval_clutch_size[1], HPDinterval_clutch_size[2]))
```

@@

```{r}
gam.plot(gamm_red.control$gam, select="Gall_Height_mm")
```

@@

control_mean_fitness <- mean(get_insect_FL.df(fl.size_control)$mean_fitness)
treatment_mean_fitness <- mean(get_insect_FL.df(fl.size_treatment)$mean_fitness)

bind_rows(mutate(get_insect_FL.df(fl.size_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.size_treatment), Treatment = "Simple")) %>%
  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Relative fitness") +
  xlab("Mean gall size\n(mm)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors)

@@

control_mean_fitness <- mean(get_insect_FL.df(fl.individuals_control)$mean_fitness)
treatment_mean_fitness <- mean(get_insect_FL.df(fl.individuals_treatment)$mean_fitness)

bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.individuals_treatment), Treatment = "Simple")) %>%
  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Relative fitness") +
  xlab("Mean gall individuals\n(mm)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors)

@@

control_mean_fitness <- mean(get_insect_FL.df(fl.density_control)$mean_fitness)
treatment_mean_fitness <- mean(get_insect_FL.df(fl.density_treatment)$mean_fitness)

bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.density_treatment), Treatment = "Simple")) %>%
  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Relative fitness") +
  xlab("Mean gall density\n(mm)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors)
